Final Project

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
Peer review!
GREAT JOB! - Maggie

filtered_fractal_data <- fractal_data %>% 
  filter(dwell_time < cutoff)
```

@@

## Building a Model (and a Plot for that Model)

@@

seq_fractal_data %>% # change points to numbers for easy sequence position identification
  ggplot(aes(x = fractal_type, y = dwell_time, color = sequence_position)) +
  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

>>>>

filtered_fractal_data <- fractal_data %>% 
  filter(dwell_time < cutoff)

```

@@

## Building a Model (and a Plot for that Model)
<!-- If you want to build a model, you might want to check the assumptions of the residuals too. -->
<!-- -From Maggie :) -->
```{r}
library(lm.beta)
library(MASS)
library(psych)
library(lmtest)

#confidence intervals:
confint(model1)
# Create a new column and append the Unstandardized model predicted values

data$pred   <- predict(model1)

# Create a new column and append the Studentized Residuals

data$zresid <- studres(model1)

# Compute the absolute value of studentized residuals

data$abs.zresid <- abs(data$zresid)

# Create a new column and append the Studentized Deleted Residuals

data$stdresid <- rstudent(model1)

# Create a new column and append the Hat Values

data$hat <- hatvalues(model1)

```

@@

seq_fractal_data %>% # change points to numbers for easy sequence position identification
  ggplot(aes(x = fractal_type, y = dwell_time, color = sequence_position)) +
  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 
  # + labs(color = "Sequence Position")
#It may be helpful to have clear labels with spaces in a final manuscript (rather than underscores). I added a legend label above.
